\section{Vision of the Solution}
% Now that we know what the customer needs, 
% what will the solution look like? 
\subsection{Vision Statement}
% This is the formal vision statement.  
%
% For:         user class
% Who:         statement of need
% The:         title of product
% Is:          statement of solution
% Unlike:      closest alternative solution
% Our Product: differentiation statement  
For on the go researchers and academics who wish to increase their available paper reading time, \TeX 2Speech will provide on-demand speech synthesis for papers and a wide variety of other scientific and technical documentation written in the \LaTeX\ format. Unlike standard TTS systems, \TeX 2Speech will be able to effectively parse a \LaTeX\ document containing mathematical equations, and convert it to comprehensible spoken word.

\subsection{Major Features}
% Describe the major features that solve the customer's needs.
Major features include the ability to take an arbitrary \LaTeX\ document and convert it into an audio representation of the text. Major commands and environments will be supported in this conversion to benefit the majority of users. The primary feature enabling this would be our implementation to convert \LaTeX\ files into Speech Synthesis Markup Language (SSML), or something similar. The marked-up file would be fed to a TTS synthesis program for the audio output. Features that will be visible to the user include the option to upload their \LaTeX\ document to our service, as well as downloading the resulting audio. 

\subsection{Assumptions and Dependencies}
% What does this product depend on?  
% The goal here is to describe, with as much detail as possible, what the envisioned
% solution needs to operate.  
It must be assumed that users have access to the internet to utilize this program. Our service will depend both on some web hosting location, along with some cloud-based TTS service, either one failing will render our service inoperable.
